### 2018-08-17 ANA-TOPQ-2017-07-PAPER-metadata.tex
update to metadata

% Comment deadline
% \AtlasCoverCommentsDeadline{DD Month 2016}

% Analysis team members - contact editors should no longer be specified
% as there is a generic email list name for the editors
\AtlasCoverAnalysisTeam{
$H \to b\bar{b}$: Trisha Farooque, Davide Gerbaudo, Aurelio Juste, Nicola Orlando,  \\ Cheng Peng,  Laura Pereira, 
Yulia Rodina, Yanjun Tu,  Lo\"ic Val\'ery, \\ Tal Van Daalen, Jia-Shian Wang, Daiki Yamaguchi; \\
$H \to \tau^+\tau^-$: Xin Chen, Antonio De Maria, Boyang Li, Ligang Xia; \\
Combination: Peter Onyisi, Harish Potti}

>>>>

% Comment deadline
\AtlasCoverCommentsDeadline{2 September 2018}

% Analysis team members - contact editors should no longer be specified
% as there is a generic email list name for the editors
\AtlasCoverAnalysisTeam{
$H \to b\bar{b}$: Trisha Farooque, Davide Gerbaudo, Aurelio Juste, Nicola Orlando,  \\ Cheng Peng,  Laura Pereira, 
Yulia Rodina, Yanjun Tu,  Lo\"ic Val\'ery, \\ Tal Van Daalen, Jia-Shian Wang, Daiki Yamaguchi; \\
$H \to \tau^+\tau^-$: Xin Chen, Antonio De Maria, Boyang Li, Ligang Xia, Gang Zhang; \\
Combination: Peter Onyisi, Harish Potti}
